### 2011-11-18 joint action and knowing others minds/interacting mindreaders.tex
minor

Note that the question a theory of interpretation answers is a question about justification.
It is not about about \emph{how} anyone actually ascribes thoughts or identifies actions. 
Nor is it (at least not immediately) a question about the mechanisms, processes or representations involved in mindreading.
To stress this, Davidson sometimes formulates the issue by asking what someone \emph{could} know that would put them in a position to know another's thoughts and actions \citep[e.g.][p.\ 126]{Davidson:1973jx}.
A theory of interpretation is just one part of an account of mindreading.

It is perhaps fair to say that most researchers regard

@@

To develop the idea that 
interaction broadens the evidential basis for interpretation
we do not need to throw away the leading, most critically examined theories of interpretation due to Davidson and Dennett.
An entirely fresh start is unnecessary.
Of course we do not mean to assert, positively, that there are not devastating objections to these theories; perhaps there are.
But considerations about the role of interaction in theories of interpretation do not give rise to any such objections.
The best way to understand how interaction bears on epistemic and normative aspects of mindreading is to extend rather than to reject the leading theories.

Since we shall discuss the role of interaction in theories of interpretation as an extension of leading theories (without any commitment here to the correctness of these theories---any theory of interpretation will have to accommodate considerations about interaction), it will be useful to start with a brief outline of those theories.

>>>>

Note that the question a theory of interpretation answers is a question about justification.
It is not about about \emph{how} anyone actually ascribes thoughts or identifies actions. 
Nor is it (at least not immediately) a question about the mechanisms, processes or representations involved in mindreading.
To stress this, Davidson sometimes formulates the issue by asking what someone \emph{could} know that would put them in a position to know another's thoughts and actions \citep[e.g.][p.\ 126]{Davidson:1973jx}.

So a theory of interpretation is just one part of a full account of mindreading.
A full account would need to address questions 
about how mindreaders actually ascribe mental states, 
about what mental states are, 
and 
about the evolution and development of mindreading,
among others.
Although a theory of interpretation will constrain and be constrained by answers to these questions,
none of these questions are directly addressed or answered by a theory of interpretation.

@@

To develop the idea that 
interaction broadens the evidential basis for interpretation
we do not need to throw away the leading, most critically examined theories of interpretation due to Davidson and Dennett.
An entirely fresh start is unnecessary.
Of course we do not mean to assert, positively, that there are no good objections to these theories; perhaps there are.
Our point is just that considerations about the role of interaction in theories of interpretation do not give rise to any such objections.
A good way to understand how interaction bears on epistemic and normative aspects of mindreading is to extend rather than to reject the leading theories.

Since we shall discuss the role of interaction in theories of interpretation as an extension of leading theories (without any commitment here to the correctness of these theories; any theory of interpretation will have to accommodate considerations about interaction), it will be useful to start with a brief outline of those theories.
